### 2020-02-13 README.Rmd
added support for topicmodels. ref #5
Fixed a inconsistency in README.Rmd
Providing statistical test for median TLO, fix #7

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm` and Warp LDA models from `text2vec`.

@@

```{r step1}
oolong_test_rater1 <- create_oolong(newsgroup_stm)
```

@@

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$lock()
```

```{r, include = FALSE}
### Mock this process
oolong_test_rater1$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater1$.__enclos_env__$private$test_content$word$intruder
oolong_test_rater1$lock()
oolong_test_rater2$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater2$.__enclos_env__$private$test_content$word$intruder
oolong_test_rater2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
oolong_test_rater2$lock()
```

@@

>>>>

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

@@

```{r step1}
oolong_test_rater1 <- create_oolong(newsgroup_stm, newsgroup5$text)
```

@@

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

```{r, include = FALSE}
### Mock this process
set.seed(46709394)
oolong_test_rater1 <- oolong:::.monkey_test(oolong_test_rater1, intelligent = 0.3)
oolong_test_rater2 <- oolong:::.monkey_test(oolong_test_rater2, intelligent = 0)
oolong_test_rater1$lock()
oolong_test_rater2$lock()
```

@@

## About the p-values

The test for model precision (MP) is based on the one-tailed, one-sample binomial test for each rater. In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a. Fisher's omnibus test).

H0: MP is not better than 1/ n\_top\_terms

H1: MP is better than 1/ n\_top\_terms

The test for the median of TLO is based on a resampling under the null hypothesis method.

H0: Median TLO is not better than random guess.

H1: Median TLO is better than random guess.

One must notice that the two statistical tests are testing the bear minimum. A significant test only indicates the topic model performs better than random guess. It is not an indication of good topic interpretability. Also, one should use a very conservative significant level, e.g. $\alpha < 0.001$.
